---
title: "delete_seqs_suggested_by_sativa"
author: "Douglas Yu"
date: "11/05/2019"
output: html_document
---

```{r}
setwd("~/src/screenforbio-mbc-ailaoshan")
```

```{r}
library(readr)
library(tidyverse)
```

Programming note:  readr can import only if the first set of lines is skipped and the column names are provided
```{r delete lrRNA sequences that sativa flags as wrong at family and above}
MIDORI_lrRNA <- read_delim("~/src/screenforbio-mbc-ailaoshan/MIDORI_lrRNA_sativa/MIDORI_lrRNA.mis", "\t", escape_double = FALSE, trim_ws = TRUE, skip = 5, col_names = c("SeqID", "MislabeledLevel","OriginalLabel","ProposedLabel","Confidence","OriginalTaxonomyPath","ProposedTaxonomyPath","PerRankConfidence"))
# the key is to skip the first set of lines
names(MIDORI_lrRNA)
MIDORI_lrRNA_sep <- MIDORI_lrRNA %>% 
    tidyr::separate(PerRankConfidence, sep = ";", into = c("domain_conf", "phylum_conf", "class_conf", "order_conf", "family_conf", "genus_conf", "species_conf"), remove = FALSE)

# save file with SeqIDs of all sequences where sativa disagrees with its taxonomic designation at the ranks of class, order, family, or subtribe. To do this, i choose all rows where MislabeledLevel != Genus or Species. These are sequences to delete.
MIDORI_locus.mis_to_delete <- MIDORI_lrRNA_sep %>% 
    filter(!MislabeledLevel %in% c("Genus", "Species")) %>% 
    select(SeqID)
write_tsv(MIDORI_locus.mis_to_delete, "~/src/screenforbio-mbc-ailaoshan/MIDORI_lrRNA_sativa/MIDORI_lrRNA.mis_to_delete", col_names = FALSE)
```

Code to replace genus and species names with sativa-suggested names, but choosing not to run this because a lot of them are probably wrong because the sativa tree will inevitably have small errors, esp. near the tips
```{r change genus and species names suggested by sativa for lrRNA, eval=FALSE, include=FALSE}
# substitute in sequences that have a sativa Confidence ≥ 0.998
# MIDORI_lrRNA_sub <- MIDORI_lrRNA %>% 
#     filter(MislabeledLevel %in% c("Genus", "Species")) %>% 
#     filter(Confidence >= 0.998) %>%
#     select(SeqID, ProposedTaxonomyPath)
# Tetrapoda.final_taxonomy_sativa.txt <- read_delim("~/src/screenforbio-mbc-ailaoshan/Tetrapoda.final_taxonomy_sativa.txt", "\t", escape_double = FALSE, col_names = c("SeqID", "ProposedTaxonomyPath"))
# 
# Tetrapoda.final_taxonomy_sativa.txt_full <- full_join(MIDORI_lrRNA_sub, Tetrapoda.final_taxonomy_sativa.txt, by = c("SeqID")) 
# Tetrapoda.final_taxonomy_sativa.txt_y <- Tetrapoda.final_taxonomy_sativa.txt_full %>%
#     filter(is.na(ProposedTaxonomyPath.x)) %>% 
#     select(SeqID, ProposedTaxonomyPath = ProposedTaxonomyPath.y)
# Tetrapoda.final_taxonomy_sativa.txt_x <- Tetrapoda.final_taxonomy_sativa.txt_full %>%
#     filter(!is.na(ProposedTaxonomyPath.x)) %>% 
#     select(SeqID, ProposedTaxonomyPath = ProposedTaxonomyPath.x)

# Tetrapoda.final_taxonomy_sativa.txt <- bind_rows(Tetrapoda.final_taxonomy_sativa.txt_x, Tetrapoda.final_taxonomy_sativa.txt_y) %>% 
#     arrange(SeqID)
# write_tsv(Tetrapoda.final_taxonomy_sativa.txt, "~/src/screenforbio-mbc-ailaoshan/Tetrapoda.final_taxonomy_sativa.txt", col_names = FALSE)
```


```{r delete srRNA sequences that sativa flags as wrong at family and above}
MIDORI_srRNA <- read_delim("~/src/screenforbio-mbc-ailaoshan/MIDORI_srRNA_sativa/MIDORI_srRNA.mis", "\t", escape_double = FALSE, trim_ws = TRUE, skip = 5, col_names = c("SeqID", "MislabeledLevel","OriginalLabel","ProposedLabel","Confidence","OriginalTaxonomyPath","ProposedTaxonomyPath","PerRankConfidence"))
# the key is to skip the first set of lines
names(MIDORI_srRNA)
MIDORI_srRNA_sep <- MIDORI_srRNA %>% 
    tidyr::separate(PerRankConfidence, sep = ";", into = c("domain_conf", "phylum_conf", "class_conf", "order_conf", "family_conf", "genus_conf", "species_conf"), remove = FALSE)

# save file with SeqIDs of all sequences where sativa disagrees with its taxonomic designation at the ranks of class, order, family, or subtribe. To do this, i choose all rows where MislabeledLevel != Genus or Species. These are sequences to delete.
MIDORI_locus.mis_to_delete <- MIDORI_srRNA_sep %>% 
    filter(!MislabeledLevel %in% c("Genus", "Species")) %>% 
    select(SeqID)
write_tsv(MIDORI_locus.mis_to_delete, "~/src/screenforbio-mbc-ailaoshan/MIDORI_srRNA_sativa/MIDORI_srRNA.mis_to_delete", col_names = FALSE)
```




Code to replace genus and species names with sativa-suggested names, but choosing not to run this because a lot of them are probably wrong because the sativa tree will inevitably have small errors, esp. near the tips
```{r change genus and species names suggested by sativa for srRNA, eval=FALSE, include=FALSE}
# # substitute in sequences that have a sativa Confidence ≥ 0.998
# MIDORI_srRNA_sub <- MIDORI_srRNA %>%
#     filter(MislabeledLevel %in% c("Genus", "Species")) %>%
#     filter(Confidence >= 0.998) %>%
#     select(SeqID, ProposedTaxonomyPath)
# Tetrapoda.final_taxonomy_sativa.txt <- read_delim("~/src/screenforbio-mbc-ailaoshan/Tetrapoda.final_taxonomy_sativa.txt", "\t", escape_double = FALSE, col_names = c("SeqID", "ProposedTaxonomyPath"))
# # 
# Tetrapoda.final_taxonomy_sativa.txt_full <- full_join(MIDORI_srRNA_sub, Tetrapoda.final_taxonomy_sativa.txt, by = c("SeqID"))
# 
# Tetrapoda.final_taxonomy_sativa.txt_y <- Tetrapoda.final_taxonomy_sativa.txt_full %>%
#     filter(is.na(ProposedTaxonomyPath.x)) %>%
#     select(SeqID, ProposedTaxonomyPath = ProposedTaxonomyPath.y)
# Tetrapoda.final_taxonomy_sativa.txt_x <- Tetrapoda.final_taxonomy_sativa.txt_full %>%
#     filter(!is.na(ProposedTaxonomyPath.x)) %>%
#     select(SeqID, ProposedTaxonomyPath = ProposedTaxonomyPath.x)
# 
# Tetrapoda.final_taxonomy_sativa.txt <- bind_rows(Tetrapoda.final_taxonomy_sativa.txt_x, Tetrapoda.final_taxonomy_sativa.txt_y) %>%
#     arrange(SeqID)
# write_tsv(Tetrapoda.final_taxonomy_sativa.txt, "~/src/screenforbio-mbc-ailaoshan/Tetrapoda.final_taxonomy_sativa.txt", col_names = FALSE)
```

